### 2016-03-21 papers.tex
Add somewhat nosy review
Revert "Add late submission on ShAIkespeare, Mona, and the Dragon"
This reverts commit abfa550609b351f0794d9d4311ba914b8ddd9417.
This paper has been withdrawn.

\addtrack{Full track}{Safety Schools of Thought}
\addpaper
	{Reducing the trusted constituent base with the LCF approach: Hillary, the next 700 elections}
	{Brandon Bohrer, Sol Boucher, and Jos Valdivida}
	{illogical, logic, Hillary, elections, congressional, fuckery, robustness, constituents, unrest, pork-barreling, curtain-closing}
	{SIGBOVIK_2016_paper_26}
	{0cm}
	{}
\addpaper
	{Unprl: Nuprl proof re-evaluation logic}
	{Ryan Kavanagh}
	{proof assistant, Nuprl, The Wizard of Oz, artificial artificial intelligence}
	{SIGBOVIK_2016_paper_11}
	{0cm}
	{}
\addpaper
	{Type-safe friends will never hurt you}
	{Brandon Bohrer}
	{friendship logic, friends, office mates, Cwelf}
	{SIGBOVIK_2016_paper_9}
	{-2cm}
	{}
\addreview{review9}{0cm}

@@

\addtrack{Lamb track}{Languages: Human and... Inhuman}
\addpaper
	{Lambda Doge: A digital canine language}
	{Joshua Suereth}
	{lambda calculus, doge, programming languages}
	{SIGBOVIK_2016_paper_15}
	{0cm}
	{}
\addpaper
	{Making the theoretical possible: the untyped $\lambda$-calculus in C++}
	{Jim McCann}
	{lambda, c++, c++11}
	{SIGBOVIK_2016_paper_23}
	{0cm}
	{}
\addpaper
	{ShAIkespeare in the modern age}
	{Abida Haque}
	{Shakespeare, AI, semantic networks, frames, intelligence}
	{SIGBOVIK_2016_paper_25}
	{0cm}
	{}
\addpaper
	{A shortmantout}
	{David Renshaw and Jim McCann}
	{portmanteausteritycoon, hotshots, cathartichokes, sadjustment}
	{SIGBOVIK_2016_paper_13}
	{0cm}
	{}

@@

\addtrack{Oversized track}{How (Over)fitting}
\addpaper
	{Reordering snacks is effective and just}
	{Dr.\ Tom Murphy VII Ph.D.}
	{snacking, permutations, comestability theory}
	{SIGBOVIK_2016_paper_8}
	{-1.2cm}
	{}
\addpaper
	{0-order Non-linear ordinary differential equations}
	{Oscar I.\ Hernandez and Daniel J.\ Packer}
	{ordinary differential equations, non-linear, nonhomo}
	{SIGBOVIK_2016_paper_5}
	{0cm}
	{}
\addpaper
	{Deep spreadsheets with ExcelNet}
	{David Fouhey and Daniel Maturana}
	{deep learning, Excel, LibreOffice, convolutional neural network, spreadsheet}
	{SIGBOVIK_2016_paper_21}
	{0cm}
	{}
\addpaper
	{Sniffing for meaning: Defining and maximizing the signal-to-nose ratio}
	{Josh Cox}
	{signal, nose, ratio, sniff, smell, scent}
	{SIGBOVIK_2016_paper_22}
	{0cm}
	{}

>>>>

\addtrack{Full track}{Safety Schools of Thought}
\addpaper
	{Reducing the trusted constituent base with the LCF approach: Hillary, the next 700 elections}
	{Brandon Bohrer, Sol Boucher, and Jos Valdivida}
	{illogical, logic, Hillary, elections, congressional, fuckery, robustness, constituents, unrest, pork-barreling, curtain-closing}
	{SIGBOVIK_2016_paper_25}
	{0cm}
	{}
\addpaper
	{Unprl: Nuprl proof re-evaluation logic}
	{Ryan Kavanagh}
	{proof assistant, Nuprl, The Wizard of Oz, artificial artificial intelligence}
	{SIGBOVIK_2016_paper_11}
	{0cm}
	{}
\addpaper
	{Type-safe friends will never hurt you}
	{Brandon Bohrer}
	{friendship logic, friends, office mates, Cwelf}
	{SIGBOVIK_2016_paper_9}
	{-2cm}
	{}
\addreview{review9}{0cm}

@@

\addtrack{Lamb track}{Languages: Human and... Inhuman}
\addpaper
	{Lambda Doge: A digital canine language}
	{Joshua Suereth}
	{lambda calculus, doge, programming languages}
	{SIGBOVIK_2016_paper_15}
	{0cm}
	{}
\addpaper
	{Making the theoretical possible: the untyped $\lambda$-calculus in C++}
	{Jim McCann}
	{lambda, c++, c++11}
	{SIGBOVIK_2016_paper_23}
	{0cm}
	{}
\addpaper
	{A shortmantout}
	{David Renshaw and Jim McCann}
	{portmanteausteritycoon, hotshots, cathartichokes, sadjustment}
	{SIGBOVIK_2016_paper_13}
	{0cm}
	{}

@@

\addtrack{Oversized track}{How (Over)fitting}
\addpaper
	{Reordering snacks is effective and just}
	{Dr.\ Tom Murphy VII Ph.D.}
	{snacking, permutations, comestability theory}
	{SIGBOVIK_2016_paper_8}
	{-1.2cm}
	{}
\addpaper
	{0-order Non-linear ordinary differential equations}
	{Oscar I.\ Hernandez and Daniel J.\ Packer}
	{ordinary differential equations, non-linear, nonhomo}
	{SIGBOVIK_2016_paper_5}
	{0cm}
	{}
\addpaper
	{Deep spreadsheets with ExcelNet}
	{David Fouhey and Daniel Maturana}
	{deep learning, Excel, LibreOffice, convolutional neural network, spreadsheet}
	{SIGBOVIK_2016_paper_21}
	{0cm}
	{}
\addpaper
	{Sniffing for meaning: Defining and maximizing the signal-to-nose ratio}
	{Josh Cox}
	{signal, nose, ratio, sniff, smell, scent}
	{SIGBOVIK_2016_paper_22}
	{0cm}
	{}
\addreview{paper22review}{-1.45cm}
